---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# `ludic`

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/ludic)](https://cran.r-project.org/package=ludic)
[![Travis-CI Build Status](https://travis-ci.org/borishejblum/ludic.svg?branch=master)](https://travis-ci.org/borishejblum/ludic)


## Overview

`ludic` is a package which performs probabilistic record linkage methods that relies on 
the use of diagnosis codes only, in the absence of direct identifiers.
On top of the [CRAN help files](https://cran.r-project.org/package=ludic), the following article explains what `ludic` is about:

> BP Hejblum, G Weber, KP Liao, N Palmer, S Churchill, P Szolovits, S Murphy, I Kohane, 
T Cai, Probabilistic Record Linkage of De-Identified Research Datasets Using Diagnosis 
Codes, 2016, *submitted*.


## Installation

The easiest way to get `ludic` is to install it from [CRAN](https://cran.r-project.org/package=ludic):
```{r CRAN-install, eval=FALSE}
install.packages("ludic")
```

Or to get the development version from [GitHub](https://github.com/borishejblum/ludic):
```{r GitHub-install, eval=FALSE}
#install.packages("devtools")
devtools::install_github("borishejblum/ludic")
```
-- Boris Hejblum